R for Clinical Study Reports and Submission

### 2022-12-08 project-folder.Rmd
Fix custom block annotation for pdf output

::: {.rmdnote}
Under the `vignettes/` folder, there are two folders: `adam/` and `tlf/`.
The `adam/` folder contains ADaM datasets.
The `tlf/` folder contains output TLFs in RTF format.
We put `adam/` and `tlf/` folders within the `vignettes/` folder only for illustration purposes.
In an actual A&R report, you may have a different location to save your input and output.
:::

@@

::: {.rmdnote}
This is the same level of reproducibility in most SAS environments:
<https://support.sas.com/techsup/pcn/altopsys.html>
:::

@@

::: {.rmdnote}
`.Rprofile` is only for project-specific R packages.
A standard R package should not use `.Rprofile`.
:::

@@

::: {.rmdnote}
RStudio Package Manager (RSPM) provides a solution to host both
publicly available and internally developed R packages.
However, the [public RSPM server](https://packagemanager.rstudio.com/client/#/repos/2/overview)
does not provide a daily snapshot as MRAN does.
:::

@@

::: {.rmdnote}
The `renv.lock` file and `renv/` folder are only for project-specific R package.
A standard R package should not use `renv`.
:::

@@

::: {.rmdnote}
A cloud-based R environment (e.g., RStudio Workbench)
can enhance the reproducibility within an organization
by using the same operating system, R version, and R package versions for an A&R project.
More details can be found at <https://environments.rstudio.com/>.
:::

::: {.rmdnote}
A container solution like Docker [@RJ-2020-007] could further enhance
the reproducibility across an organization at the operating system level
but beyond the scope of this book.
:::

>>>>

::: {.rmdnote data-latex=""}
Under the `vignettes/` folder, there are two folders: `adam/` and `tlf/`.
The `adam/` folder contains ADaM datasets.
The `tlf/` folder contains output TLFs in RTF format.
We put `adam/` and `tlf/` folders within the `vignettes/` folder only for illustration purposes.
In an actual A&R report, you may have a different location to save your input and output.
:::

@@

::: {.rmdnote data-latex=""}
This is the same level of reproducibility in most SAS environments:
<https://support.sas.com/techsup/pcn/altopsys.html>
:::

@@

::: {.rmdnote data-latex=""}
`.Rprofile` is only for project-specific R packages.
A standard R package should not use `.Rprofile`.
:::

@@

::: {.rmdnote data-latex=""}
RStudio Package Manager (RSPM) provides a solution to host both
publicly available and internally developed R packages.
However, the [public RSPM server](https://packagemanager.rstudio.com/client/#/repos/2/overview)
does not provide a daily snapshot as MRAN does.
:::

@@

::: {.rmdnote data-latex=""}
The `renv.lock` file and `renv/` folder are only for project-specific R package.
A standard R package should not use `renv`.
:::

@@

::: {.rmdnote data-latex=""}
A cloud-based R environment (e.g., RStudio Workbench)
can enhance the reproducibility within an organization
by using the same operating system, R version, and R package versions for an A&R project.
More details can be found at <https://environments.rstudio.com/>.
:::

::: {.rmdnote data-latex=""}
A container solution like Docker [@RJ-2020-007] could further enhance
the reproducibility across an organization at the operating system level
but beyond the scope of this book.
:::

### 2022-12-08 tlf-overview.Rmd
Fix custom block annotation for pdf output

::: {.rmdnote}
FDA's PDF specification is a general reference. Each organization can define
more specific TLF format requirements that can be different from the examples in this book.
:::

@@

::: {.rmdnote}
There are other R packages to create TLFs in ASCII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Readers are encouraged to explore other R packages to find the proper tools to fit your purpose. 
:::

>>>>

::: {.rmdnote data-latex=""}
FDA's PDF specification is a general reference. Each organization can define
more specific TLF format requirements that can be different from the examples in this book.
:::

@@

::: {.rmdnote data-latex=""}
There are other R packages to create TLFs in ASCII, RTF and Word format.
For example, `rtables`, `huxtable`, `pharmaRTF`, `gt`, `officer`, `flextable` etc.
Here we focus on `r2rtf` to illustrate the concept.  
Readers are encouraged to explore other R packages to find the proper tools to fit your purpose. 
:::
